Paper 2 !DRAFT! Do not circulate!

### 2014-12-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Fixed a naming bug.

<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(x=delta, y=sigma, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma)) +
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

@@

<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
standardTriPlot(data=cesCoeffsDataX, 
                mapping=aes(color=Source), 
                facet_formula=country~nestStrParen) +
  guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

>>>>

<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
standardScatterPlot(data=subset(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(x=delta, y=sigma, color=Source), 
                    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma)) +
    guides(colour=guide_legend(override.aes = aes(alpha=1)))
@

@@

<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
standardTriPlot(data=cesCoeffsDataXp, 
                mapping=aes(color=Source), 
                facet_formula=country~nestStrParen) +
  guides(colour=guide_legend(override.aes = aes(alpha=1)))
@
